A Hybrid Ensemble Learning Approach to Star-galaxy Classification

### 2015-03-30 paper/main.tex
remove table 1.

One of the most important parameter in \texttt{SOMc}
is the topology of the two-dimensional SOM,
which can be rectangular, hexagonal, or spherical.
To classify stars and galaxies in the CFHTLenS data,
we use a spherical topology,
which is constructed by using
\texttt{HEALPIX}~\citep{gorski2005healpix}.
Furthermore, similar to \texttt{TPC},
we use the OOB technique to make an unbiased estimation of errors.
For a complete description of the SOM implementation
and its application to the estimation of
photo-$z$ probability distribution funtions,
we refer the reader to \cite{carrascokind2014somz}.

@@

One of the most common methods to classify a source
based on its observed magnitudes is template fitting.
Template fitting algorithms are unsupervised;
there is no need for additional knowledge outside the
observed data and the template SEDs.
However, any incompleteness in our knowledge of the template SEDs
that fully span the possible SEDs of observed sources
may lead to misclassification of sources.

@@

We therefore adopt the binning strategy similar to 
\cite{carrascokind2014exhausting}.
In this binning strategy,
we allow different classifier combinations 
in different parts of parameter space
by creating two-dimensional SOM representations of
the full nine-dimensional magnitude-color space.
A SOM representation can be rectangular, hexagonal, or spherical;
here we choose a 10$\times$10 rectangular topology to facilitate 
visualization as shown in Figure.~\ref{fig:som_colors}.
For all combination methods,
we use only the OOB (cross validation) data contained in each cell
to compute the relative weights for the base classifiers.
The weights within individual cells are then applied to the test data
to make the prediction.

@@

For binary classifiers whose output is either zero or one
(\eg a cut-based morphological separation),
we assume that each example is corrupted with
an average error rate $\epsilon$.
This means that
$P\left(d|e\right) = 1-\epsilon$ if the combination $e$
correctly predicts class $\hat{y}_i$ for the $i^{\text{th}}$ object,
and $P\left(d|e\right) = \epsilon$ if it predicts an incorrect class.
The average rate $\epsilon$ can be estimated by
the fraction $\left(M_g + M_s\right) / N$,
where $M_g$ are $M_s$ are defined in Table~\ref{table:def_numbers},
and $N$ is the total number of sources.
Equation~\ref{eq:p_ensemble} then becomes

@@

\begin{table}
  \caption{The definition of the number of stars/galaxies
           classified and misclassified as stars/galaxies.}
  \centering
  \begin{tabular}{ l | c | c }
    \hline
                           & True galaxies & True stars \\ \hline
    Classified as galaxies & $N_g$ & $M_s$ \\ \hline
    Classified as stars & $M_g$ & $N_s$ \\
    \hline
  \end{tabular}
  \label{table:def_numbers}
\end{table}

@@

\noindent
where $N_g$ and $M_g$ are define in Table~\ref{table:def_numbers}.
We define the galaxy \textit{purity} $p_g$ (also known as precision
or positive predictive value)
as the fraction of the number of true galaxies classified as galaxies
out of the total number of objects classified as galaxies, 
\begin{equation}
p_g = \frac{N_g}{N_g + M_s},
\end{equation}

\noindent
where $N_g$ and $M_g$ are define in Table~\ref{table:def_numbers}.
Star completeness and purity are defined in a similar manner.

>>>>

One of the most important parameter in \texttt{SOMc}
is the topology of the two-dimensional SOM,
which can be rectangular, hexagonal, or spherical.
To classify stars and galaxies in the CFHTLenS data,
we use a spherical topology,
which is constructed by using
\texttt{HEALPIX}~\citep{gorski2005healpix}.
Furthermore, similar to \texttt{TPC},
we use the OOB technique to make an unbiased estimation of errors.
For a complete description of the SOM implementation
and its application to the estimation of
photo-$z$ probability distribution functions,
we refer the reader to \cite{carrascokind2014somz}.

@@

One of the most common methods to classify a source
based on its observed magnitudes is template fitting.
Template fitting algorithms do not require a spectroscopic training sample;
there is no need for additional knowledge outside the
observed data and the template SEDs.
However, any incompleteness in our knowledge of the template SEDs
that fully span the possible SEDs of observed sources
may lead to misclassification of sources.

@@

We therefore adopt the binning strategy similar to 
\cite{carrascokind2014exhausting}.
In this binning strategy,
we allow different classifier combinations 
in different parts of parameter space
by creating two-dimensional SOM representations of
the full nine-dimensional magnitude-color space:
$u$, $g$, $r$, $i$, $z$, $u-g$, $g-r$, $r-i$, and $i-z$.
A SOM representation can be rectangular, hexagonal, or spherical;
here we choose a 10$\times$10 rectangular topology to facilitate 
visualization as shown in Figure.~\ref{fig:som_colors}.
For all combination methods,
we use only the OOB (cross validation) data contained in each cell
to compute the relative weights for the base classifiers.
The weights within individual cells are then applied to the test data
to make the prediction.

@@

For binary classifiers whose output is either zero or one
(\eg a cut-based morphological separation),
we assume that each example is corrupted with
an average error rate $\epsilon$.
This means that
$P\left(d|e\right) = 1-\epsilon$ if the combination $e$
correctly predicts class $\hat{y}_i$ for the $i^{\text{th}}$ object,
and $P\left(d|e\right) = \epsilon$ if it predicts an incorrect class.
The average rate $\epsilon$ can be estimated by
the fraction $\left(M_g + M_s\right) / N$,
where $M_g$ is the number of true galaxies classified as stars,
$M_s$ is the number of true stars classified as galaxies,
and $N$ is the total number of sources.
Equation~\ref{eq:p_ensemble} then becomes

@@

%%\begin{table}
%%  \caption{The definition of the number of stars/galaxies
%%           classified and misclassified as stars/galaxies.}
%%  \centering
%%  \begin{tabular}{ l | c | c }
%%    \hline
%%                           & True galaxies & True stars \\ \hline
%%    Classified as galaxies & $N_g$ & $M_s$ \\ \hline
%%    Classified as stars & $M_g$ & $N_s$ \\
%%    \hline
%%  \end{tabular}
%%  \label{table:def_numbers}
%%\end{table}

@@

\noindent
where $N_g$ is the number of true galaxies classified as galaxies
and $M_g$ is the number of true galaxies classified as stars.
We define the galaxy \textit{purity} $p_g$ (also known as precision
or positive predictive value)
as the fraction of the number of true galaxies classified as galaxies
out of the total number of objects classified as galaxies, 
\begin{equation}
p_g = \frac{N_g}{N_g + M_s},
\end{equation}

\noindent
where $M_s$ is the number of true stars classified as galaxies.
Star completeness and purity are defined in a similar manner.
